Video vision-language models (VLMs) already receive evidence about what stayed
still, what moved, and what is new. Most stacks discard that structure, hand the
model dense RGB again, and ask it to rediscover state it could have reused. The
factory wall did not move, the stream has cheap evidence that it did not move,
and the stack still pays again for dense visual or prefix computation. We study
that waste as training-free anti-recomputation.

The broadest repaired follow-up result appears after the video has already been ingested. On
frozen Qwen2.5-VL-7B-Instruct-4bit, adaptive same-video follow-up reuse repairs
20-frame short, medium, and long VideoMME slices plus a 32-frame short slice
with no observed paired choice or correctness drift on 93 paired queries,
including 62 repaired follow-ups. Same-class follow-up speedup is
14.90--35.92$\times$ when cold follow-ups are compared with repaired
follow-ups within matched frame/duration cells; the cold-all-query versus
repaired-follow-up ratio is 15.28--35.97$\times$ when the cold baseline's
per-query cost is compared with repaired follow-up latency. The mechanism is concrete: the second follow-up inherits
the cache repaired after the first follow-up, so it appends mostly the new
question instead of repairing the newest-frame tail again. This is not
first-query speedup: the first query still pays full freight, and the tested
sessions have two follow-up questions per video. A separate many-turn stress on
seven 20-frame short videos then cycles the same questions through 50 turns:
adaptive repair and scheduled refresh have no observed paired drift on 343
follow-ups, while fixed \(K=1\) remains below the 3\% drift gate but shows
nonzero choice/correctness drift in the repeated-question schedule. A stricter
dense-answer-anchored prompt-variation stress gives the boundary:
conservative fixed \(K=1\) remains 0/133 on follow-ups through 20 turns,
while adaptive repair and refresh-10 each show 6/133 paired choice/correctness
drift (4.51\%) in exchange for roughly 0.7\,s follow-up latency. Aggressive
reuse is therefore a high-speed operating point, not a universal
correctness-preserving policy.

The central question is where a runtime must buy fresh visual evidence over
time, and where cached state is enough to remain on its regime-specific
quality--compute frontier. That question only makes sense if the accounting is
honest. We evaluate frozen
VLMs with MLX-backed VideoMME, MVBench, and TOMATO protocols, plus a separate
26B-class streaming protocol, and we keep the regimes separate: first-pass
visual work on fresh videos, after-ingest follow-up questions about the same
video, and streaming workloads that revisit nearly the same visual state. They
are not interchangeable. \emph{Stage-share ceiling (C-CEILING)} formalizes the
bound: a component win becomes an end-to-end win only in proportion to the
wall-clock share it actually accelerates. This is why the n=60 composition
audit is a ceiling-matched null rather than a multiplier.

\emph{Persistent follow-up reuse (C-PERSIST)} is the name we give to this
after-ingest regime. It reuses the already-paid prompt/key--value (KV)
attention state for later questions about the same video. Unrepaired reuse
eventually enters a cache basin, a failure region where reused state drives
repeated answer drift or
pathological outputs. Selective re-prefill refreshes a small newest-frame
visual tail and restores the tested follow-up contract. Fixed \(K=1\) remains
the no-coordination baseline at 9.48--20.37$\times$ same-class speedup with no
observed paired drift on the same 93-query envelope.

Fresh-video pruning is smaller but measured. \emph{First-pass vision pruning
(C-VISION)} reduces work inside the VLM vision tower, the visual encoder that
turns frames into model tokens, during the first query on a fresh video. The
clean VideoMME holdout cell gives 1.113$\times$ first-pass wall-clock gain
with zero aggregate accuracy delta; advisory MVBench and TOMATO holdout cells
are larger but carry timing and accuracy caveats. Measured sparse vision
execution makes the first-pass story sharper: on Gemma 4-E4B-4bit 32f short,
the runtime skips timed vision-tower work at 1.316$\times$ first-query speedup
with no paired drift on 20 items and no parse failures. The full Gemma 8/16/32f sweep
has zero paired answer drift but matched dense/sparse parse failures in some
cells; Qwen is configuration-sensitive. A Qwen 8f keep-rate sweep tracks the
C-CEILING timing prediction tightly even when all cells fail the fidelity
contract; a conservative 16f operating point recovers to within the
aggregate-accuracy and format gates at
1.032$\times$ with only 13.6\% vision-time reduction. These are measured
sparse-execution envelopes, not a license to multiply every component win.
The routing audits explain why those numbers are not the whole story:
local diagnostics suggest fresh-compute placement is not captured by novelty
magnitude alone,
aggregate accuracy can hide answer-identity drift, and cached-feature
substitution tests answer preservation rather than measured sparse execution.

Streaming state reuse (candidate C-STREAM) is the native-rate version of the
same question, but it is not yet a headline claim. A 26B-class
scale-out evaluation makes the lane more concrete and more bounded:
default mixed sliding-window/full-attention
cache reuse fails a cross-turn correctness smoke, a topology-aware warm-prefix
snapshot (a saved post-ingest cache state used only for follow-up timing)
gives positive small-\(N\) follow-up rows, fixed-evidence streaming
baselines favor low-FPS dense over the tested event-window proxy, and the
large exactness audit separates zero accuracy delta on 1,937 rows from
byte-identical raw-paired text on 513 rows.

The broader implication is not that pixel differencing is the final interface.
The experiments are a requirements probe for future VLM-native media streams:
systems that expose change, motion, uncertainty, object state, sensor time, and
active tiles directly, so the model does not have to rediscover the world from
dense RGB every frame.
