\section{Introduction}

Video vision-language models (VLMs) spend a surprising amount of time
rediscovering what they already know. The wall behind a factory robot did not
move. The stove, countertop, or
security-camera background often did not move either. A vehicle's front camera
also sees much of the world move predictably: nearby objects expand, lane
markers flow outward, and the surprise is concentrated near boundaries,
occlusions, and independent movers. The video stream carries cheap evidence of
stasis, motion, and residual surprise, and classical codecs have spent decades
turning that evidence into compact state. Yet most VLM pipelines hand the model
another dense stack of RGB frames and ask it to pay again for vision encoding,
prefill, or both.

That repeated payment is the seed of this paper. A benchmark clip is sampled
into several frames, many of those frames are visually redundant, and the stack
still treats them as fresh. The same waste appears in repeated follow-up
questions on the same video, and it becomes even more obvious in live streams
where most of the scene remains stable for long stretches. The interesting
question is no longer whether redundancy exists. It does. The question is
where that redundancy can be removed without breaking the answer.
The largest measured opportunity is after ingest: repaired same-video
follow-up reuse reaches 14.90--35.92$\times$ speedup with no observed paired
drift on 62 repaired follow-ups in the tested breadth envelope.

Our central question is where a VLM must buy fresh visual evidence over time,
and where cached state is enough to stay on the relevant regime-specific
quality--compute frontier. The key variable is not simply how much visual
compute is reused. A small transient event, a moving hand, a text flash, or an
object entering at a boundary can matter more than a large region of
predictable background motion. The planner buys fresh evidence; the model
still decides what matters.

The literature often treats that waste as if it were one knob. It is not. The
fresh-video pass is bounded by whatever share of wall-clock the vision tower
actually owns. After-ingest follow-up queries on the same video are a
different regime: once the prefix has been paid, prompt reuse can dominate.
Routing under a fixed dense backend is different again: it tells us whether a
training-free policy preserves answer quality, not whether the backend has
already been rewritten to skip timed work. Reuse is three regimes with three
different ceilings, not one multiplier that can be copied from paper to paper.

That distinction changes what the paper is about. The first contribution is
\emph{persistent follow-up reuse (C-PERSIST)}: the after-ingest same-video
regime where the biggest local multipliers already exist, but also where cache
reuse enters a measurable basin unless the visual tail is repaired. The second
is \emph{stage-share ceiling (C-CEILING)}: an arithmetic guardrail on how much
of a local speedup can survive to end-to-end wall-clock. The third is
\emph{first-pass vision pruning (C-VISION)}: measured first-pass gains on
fresh videos via training-free vision-tower pruning. Candidate C-STREAM stays
in the paper as the native-rate state-update target and boundary evidence, not
as a fourth headline; Qwen routing remains mechanism evidence under a fixed
dense backend.

The larger target is not a bigger threshold sweep and not a new codec in this
paper. The experiments here are a measurement instrument: they ask which
cheap temporal signals are already useful to a frozen VLM runtime, where those
signals fail, and what a future VLM-native media stream should expose directly.
Codec and pixel signals are therefore treated as freshness and uncertainty
signals, not as semantic-saliency oracles. They can say where something
probably changed; the model and the task still decide what matters. That is
why the VLM-native media discussion later in the paper is framed as candidate
requirements, not as a systems claim here.

The same boundary applies to training. These are training-free inference
experiments, not measured training-speedup experiments. The training-relevant
claim is narrower and more useful: the traces identify where frozen models
already tolerate reuse, where they do not, and what a future model could learn
as native refresh gates, delta encoders, or cache-state-aware attention.

The scale-out streaming lane is part of the same science story, but it has a
different protocol. A checked 26B-class bundle sharpens the boundary rather
than simply adding wins: the default cross-turn cache path is unsafe,
topology-aware warm-prefix snapshot rows (saved post-ingest cache states used
only for follow-up timing) are positive at small \(N\), and
fixed-evidence streaming baselines show that low-FPS dense is a serious
competitor. We keep this as candidate C-STREAM: boundary evidence and gates for
future native-rate state reuse, not a multiplier to inherit. The same warning
shows up locally in Qwen session-composition experiments, where speedup can
survive while the full follow-up fidelity contract does not.

\begin{table}[H]
\centering
\caption{Reuse regime map. Rows are separate workloads and denominators, not
one multiplier. Candidate C-STREAM is a deployment target and boundary lane;
routing under a fixed dense backend is mechanism evidence rather than a sparse
wall-clock claim.}
\label{tab:three-regimes}
\footnotesize
\renewcommand{\arraystretch}{\PaperTableStretch}
\begin{tabularx}{\linewidth}{@{}
  >{\raggedright\arraybackslash}p{0.18\linewidth}
  >{\raggedright\arraybackslash}p{0.23\linewidth}
  >{\raggedright\arraybackslash}p{0.22\linewidth}
  >{\raggedright\arraybackslash}X
@{}}
\toprule
Regime & Reused work & Denominator / gate & Evidence / boundary \\
\midrule
After-ingest follow-up & prompt / key--value (KV) prefix for later questions on the same video & follow-up latency and paired drift; first query still pays full freight & raw 16f reuse reaches 91.1$\times$; adaptive repair spans short/medium/long and 32f-short with 0/93 drift at 14.90--35.92$\times$; many-turn stress reaches 50 turns on repeated questions; dense-answer-anchored prompt variation exposes the conservative/aggressive boundary \\
Fresh-video first pass & vision-tower work inside the first query & first-query wall-clock; clean/advisory gates plus measured sparse-execution envelopes & VideoMME clean 1.113$\times$; MVBench/TOMATO advisory; measured sparse vision: Gemma 32f short 1.316$\times$ with 0/20 drift, Qwen conservative boundary 1.032$\times$ \\
Candidate C-STREAM & repeated visual state in a native-rate or live pipeline & checked mixed evidence bundle; separate protocol & default 26B cache path blocked; prefix-snapshot rows positive but small-\(N\); fixed-evidence stream baselines favor low-FPS dense over the tested proxy \\
\bottomrule
\end{tabularx}
\end{table}

The table is a workload map. The contributions below are the analytical and
empirical pieces that explain those workloads without collapsing them into a
single multiplier. We make three contributions:
\begin{itemize}[leftmargin=1.5em]
\item We characterize \textbf{persistent follow-up reuse (C-PERSIST)}: after-ingest persistent-KV reuse on
Qwen collapses follow-up latency to roughly conversational timescales, with a
7B tested envelope through 16 frames / 6.5k prefill tokens, a clean 16f point,
and a wider but bounded 3B plateau through 36 frames / 14.5k prefill tokens.
We then show that the 7B basin is repairable: selective re-prefill of a fixed
newest-frame visual tail gives no observed paired choice or correctness drift
on 93 paired queries spanning short, medium, long, and 32-frame short slices,
while retaining 9.48--20.37$\times$ follow-up speedup. A state-aware adaptive
variant repairs once and lets the next follow-up inherit that repaired state;
across the same 93-query breadth, it has no observed paired drift and reaches
14.90--35.92$\times$ same-class follow-up speedup
(15.28--35.97$\times$ cold-all-query / repaired-follow-up ratio). Stress tests
bound that win: repeated-question schedules show no adaptive cliff through 50
turns, while dense-answer-anchored prompt variation keeps conservative
fixed \(K=1\) paired-drift clean but exposes 6/133 paired drift for aggressive
policies.
\item We derive and validate \textbf{stage-share ceiling (C-CEILING)}: a
guardrail for end-to-end gain. The same arithmetic explains both the modest first-pass
multipliers and the n=60 composition audit, where the observed
1.042$\times$ stacked result lands almost exactly where the measured share
terms predict.
\item We establish \textbf{first-pass vision pruning (C-VISION)}: training-free mid-layer vision-tower
pruning yields measured first-pass end-to-end gains on frozen Gemma video-VLM
runs, from a clean 1.113$\times$ VideoMME holdout to advisory larger cells,
with magnitude governed by the vision-share ceiling rather than wishful
component-wise multiplication. The measured sparse-execution envelope then
separates systems truth from fidelity truth: Gemma 32f short is a clean
1.316$\times$ timed-skip cell, while Qwen's 8f keep-rate sweep validates the
timing ceiling despite fidelity failure and its conservative 16f point
recovers to within the aggregate-accuracy/format gates only at low gain.
\end{itemize}

Those three contributions do not compose as a naive product. C-VISION changes
first-pass latency. C-PERSIST changes follow-up latency on later queries about
the same video. C-CEILING says shared stage budgets cannot be spent twice. The
paper therefore reports composition against measured ceilings, not against
headline multiplication.

Qwen routing and its preserved nulls are what keep that framing honest. The
holdout planner results show a real quality--compute frontier under a frozen
dense backend, local novelty-ranked dense diagnostics suggest that quantity
alone is the wrong variable, and the VideoMME frame-count probes show that
``more frames'' is not a linear quality knob on the Qwen stack. The dev-split
16-frame
long-bucket regression does \emph{not} replicate on disjoint holdout; that is
exactly the kind of boundary the paper keeps instead of smoothing away.
The same discipline applies to paired drift: several runs preserve
aggregate accuracy while changing individual answers, so the paper reports
choice diffs, correctness diffs, pathological-attractor counts, and confidence
intervals whenever they decide the claim boundary.
