\section{Related Work}

The closest systems neighbor is CodecSight \cite{codecsight}, which also tries
to avoid unnecessary visual processing by using compressed-video structure
before the rest of the model consumes the content. The difference is both in
signal and in target. CodecSight uses decoder-native motion vectors and
residuals and is evaluated on streaming anomaly detection; our current local
implementation uses a pixel-domain proxy because that is what our MLX stack can
exercise today, and our main benchmark evaluations target temporal-reasoning QA
on TOMATO \cite{tomato} and MVBench \cite{mvbench}.

Trained codec-native approaches answer a different question. CoPE-VideoLM
\cite{copevideolm}, Deja Vu \cite{dejavu}, and older compressed-video pipelines
such as CoViAR \cite{coviar} learn how motion, residual, or reused
representations should enter the model. That is valuable prior art, but it does
not settle the deployment question we care about here: how much redundancy a
frozen stack can exploit before retraining or representation learning enters
the picture.

Another family reduces visual cost after tokens already exist. FastV
\cite{fastv}, FastVID \cite{fastvid}, FlashVID \cite{flashvid}, VisionZip
\cite{visionzip}, SparseVLM \cite{sparsevlm}, VScan \cite{vscan}, STTM
\cite{sttm}, SparseVILA \cite{sparsevila}, and LLaVA-PruMerge
\cite{llavaprumerge} prune, retrieve, or merge visual tokens using
attention-derived, density, query-aware, or feature-similarity signals. ToMe
\cite{tome} is the older training-free ViT token-merging ancestor, and
EvoPrune \cite{evoprune} is a late-breaking MLLM example of pruning inside
the visual encoder itself. Those methods are adjacent but not identical to our
setting. Their signal usually lives after visual tokens exist, or changes the
encoder/runtime contract. Our routing lane asks an earlier question: can we
decide where fresh computation should land in time before the full dense
backend pays for every frame again? Our first-pass pruning lane then adds a
different discipline: the speedup must be interpreted through the measured
stage-share ceiling, not through the component multiplier alone.

Temporal redundancy inside vision transformers is also prior art. Eventful
Transformers \cite{eventful} reprocess only tokens that changed significantly
between frames, often without retraining. That makes it a useful north star for
measured sparse execution. Our local Track-B evidence is deliberately narrower:
it verifies that a Qwen sparse-ViT path can skip timed vision work and that the
ceiling predicts the timing, while also reporting the current fidelity failure.

Long-horizon reuse and systems co-design are directly relevant. QuickVideo
\cite{quickvideo} explicitly co-designs decode and prefill. ReKV \cite{rekv},
VLCache \cite{vlcache}, StreamingVLM \cite{streamingvlm}, SparseVILA
\cite{sparsevila}, and HERMES \cite{hermes} study cached visual or KV state
over long contexts, streaming video, or multi-turn multimodal inference.
SGLang's RadixAttention \cite{sglang}, vLLM/PagedAttention \cite{vllm}, and
standard prefix caching show that shared-prefix KV reuse is already a serving
systems primitive; C-PERSIST should not be read as inventing that primitive.
CacheBlend \cite{cacheblend} is even closer to the repair pattern: it reuses
bulk cached KV for RAG contexts and selectively recomputes part of the cache to
restore quality. Our contribution is the video-VLM instantiation and boundary:
which visual tail to refresh, the cache-basin failure mode, the paired-drift
contract, and the post-\(Q2\) inheritance rule that separates the failed and
successful adaptive variants.

Efficient VLM architectures such as FastVLM \cite{fastvlm} attack the same
latency pressure by changing the visual encoder and tokenization. They are
complementary to this paper rather than baselines for a frozen-stack claim:
our experiments ask what a deployed VLM can avoid recomputing without changing
weights, while C-CEILING explains when even a large component win can remain a
modest request-level win.

SimpleStream \cite{simplestream} is also an important streaming baseline
because it argues that a strong recent-frame window can match or outperform
heavier streaming-memory systems on modern benchmarks. That critique matters
directly for our streaming lane: any cache or memory mechanism has to beat a
strong recency baseline under matched budget, not just beat a strawman.

More conceptually, our framing is adjacent to approximate computing
\cite{rinardapprox}: skipping work under an explicit quality budget. The
difference is that the skipped work here is temporal visual recomputation, and
the guardrail is benchmark fidelity rather than an application-specific numeric
tolerance.

Our position is therefore narrower and more explicit than a generic
``efficient-video-VLM'' claim. We study training-free anti-recomputation for
frozen video VLMs, separating first-pass reuse, after-ingest reuse, and
mechanism-validation routing. The paper is not a claim that pixel differencing
is the final signal. It is a claim that careful temporal reuse is already worth
studying before codec-native systems are available in this stack.

\begin{sectiontodo}{Freeze the final comparison table against the primary papers}
The mechanism families are now in the right buckets, but a submission version
still needs a tighter final comparison table with exact titles, venues, and one
checked headline metric per cited method.

\textcolor{todoBorder}{Source pointers: \path{docs/related-work-table.md},
\path{docs/literature-map-2026-04-16.md},
\path{paper/framing.md}.}
\end{sectiontodo}
