\section{Method}

\subsection{Problem Setting}

We study three deployment regimes on frozen video-VLM stacks, plus a separate
routing path used for mechanism validation:

\begin{itemize}[leftmargin=1.5em]
\item \textbf{First-pass visual pruning:} skip or reduce vision-tower work
before the rest of the model pays for it.
\item \textbf{After-ingest follow-up reuse:} keep the expensive prefix from the
first query and ask the next question against the same video.
\item \textbf{Streaming / deployment reuse:} revisit repeated visual state in
a native-rate or live pipeline.
\item \textbf{Routing under a fixed dense backend:} substitute cached visual
state to test whether answer quality survives, even when the benchmark path has
not yet been rewritten into a sparse wall-clock implementation.
\end{itemize}

These are related, but they are not interchangeable. They are kept
analytically separate because they measure different kinds of reuse.

\subsection{Reader's Map of the Session Terms}

The session experiments are easier to read with the naming convention stated
up front. A \emph{cold} query recomputes the full video prefix. A
\emph{follow-up} query asks another question about the same video after that
prefix has already been ingested. In the Qwen session experiments, \(Q0\) or
\(Q1\) denotes the first question on a video, while \(Q2\) and \(Q3\) are later
questions in the same three-query session. The symbol \(K\) is the number of
newest visual frames re-prefilled before a follow-up; \(K=1\) means ``refresh
one newest frame, reuse the rest of the prefix.'' A \emph{same-class speedup}
compares cold follow-up queries to session follow-up queries. An
\emph{all-query denominator} compares all cold queries to session follow-ups;
we report it only when the text says so explicitly.

The main safety metric is \emph{paired drift}. A run has no observed paired
choice drift when each session answer chooses the same multiple-choice option
as its matched cold baseline. It has no observed paired correctness drift when
each answer is right or wrong on the same examples as the baseline. This is
stronger than matching aggregate accuracy, but it is still a finite-sample
observation, not a population proof.

\subsection{Temporal Planner}

For adjacent frames, the routing path computes a per-block statistic on the RGB
difference plane. The implementation supports mean difference, max-absolute
difference, changed-pixel fraction, and top-$k$ mean over the block. In the
best current clean-tree Qwen policy, the statistic is \texttt{max\_abs}. Fixed
thresholds partition blocks into \emph{static}, \emph{shifted}, and
\emph{novel} regions. These names are historical planner labels, not literal
codec semantics: today they mean low, medium, and high pixel-domain change.

The block geometry is derived from the model's vision configuration rather than
hard-coded. On Qwen2.5-VL, planner decisions line up with the merged-token
spatial grid so cached features can be substituted back into the dense path at
the same geometry the benchmark runner already understands.

The paper's default sparse-QA routing path still uses pixel differences because
that is the audited semantic baseline. A separate codec-native planner bridge
now exists locally: continuous H.264-derived scores can substitute for the
pixel-diff planner signal on VideoMME dev all-duration \(n=30\) without
changing dense answer choices, and calibration-mode/source ablations are
neutral on the local slices. We keep this as semantic planner-substitution
evidence, not a latency claim, because the current offline extraction retrofit
is much slower than the sparse frame-sampling path; a systems claim requires a
streaming decoder-integrated path.

\subsection{Bounded Staleness}

Reuse without age control drifts. The planner therefore carries a
bounded-staleness counter: even a block that continues to look reusable must be
refreshed after its age exceeds a configured limit. The clean-tree policy used
in the paper sets that limit to four frame steps. That choice is not cosmetic.
It is the main reason the planner survives TOMATO, where temporally concentrated
evidence punishes policies that keep trusting a stale region simply because the
local pixel difference remains small.

We summarize routing budget by converting block-level reuse into an effective
fresh-frame count,
\[
f_{\mathrm{eff}} = 1 + (N - 1)(1 - r_{\mathrm{reuse}}),
\]
where $r_{\mathrm{reuse}}$ is the mean active-region reuse ratio. This gives
the Qwen routing results a common x-axis with dense-$N$ baselines: how much
fresh visual budget the policy effectively spent.

\subsection{Vision-Tower Pruning and Persistent-KV}

The other two mechanisms operate at different points in the stack.

The Gemma path patches the vision tower after an internal layer, keeps only a
fraction of the tokens, and scatters the result back so downstream geometry is
unchanged. The resulting first-pass speedup is constrained by how much of total
wall-clock the vision tower owns. More generally, if a method accelerates only
one stage of a pipeline by a factor $s$, and all other stages are held fixed,
the ideal end-to-end gain is
\[
\mathrm{E2E}_{\mathrm{ideal}} =
\frac{1}{f_{\mathrm{fixed}} + (1 - f_{\mathrm{fixed}}) / s},
\]
where $f_{\mathrm{fixed}}$ is the dense wall-clock fraction left untouched.
That is the paper's C-CEILING contribution: the denominator limits how much of
a local speedup can survive. In real runs, residuals around this model expose
overhead, scheduler noise, thermal movement, or non-target stages that moved
despite the intended intervention. For vision-tower pruning, the same logic
reduces to the scatter-back prediction
\[
\mathrm{E2E}_{\mathrm{pred}} =
\frac{1}{1 - V_{\mathrm{share}} V_{\mathrm{red}}},
\]
where $V_{\mathrm{share}}$ is the dense vision share and $V_{\mathrm{red}}$ is
the observed reduction in vision time.

The persistent-KV path answers a different question. Here the user has already
paid for the first query on a video. The next question about that same video
reuses the prompt cache and only appends a short textual suffix. The result can
be dramatically faster, but it is explicitly an \emph{after-ingest} claim. It
is not a claim about faster first-pass understanding of fresh videos.

Persistent reuse also has a repair path. When a long visual prefix falls into a
cache-reuse basin, the selective re-prefill runner keeps the reusable text and
old visual prefix, refreshes a fixed newest-frame visual tail, and continues the
follow-up from that repaired state. The knob \(K\) is the number of newest
visual frames re-prefilled on each follow-up. Larger \(K\) spends more latency
to repair more visual context; smaller \(K\) approaches the deployment-speed
regime. This is still after-ingest reuse: the first query remains cold, and the
claim is about later questions on the same video.

\subsection{Paired Drift Metrics}

Aggregate accuracy is not a sufficient safety metric for reuse. A cached or
pruned run can keep the same aggregate score while changing individual answer
choices, and a follow-up cache can lose accuracy by collapsing into a
pathological output distribution rather than by making ordinary wrong choices.
The paper therefore records paired choice diffs, paired correctness diffs,
parse failures, degenerate or pathological-like outputs, and query-index splits
whenever these decide the claim. The distinction matters scientifically:
answer-identity drift, accuracy drift, and format collapse point to different
repair mechanisms.

\subsection{What Is Actually Skipped}

The paper keeps semantic substitution and wall-clock skipping separate. The
Qwen routing runner can replay or substitute cached features to test whether the
answer survives. That is enough to study the quality--compute frontier. It is
not enough to claim an end-to-end speedup until the backend itself skips timed
work. The Gemma and persistent-KV lanes do change measured wall-clock and
therefore support speedup claims. The Qwen routing lane does not yet. The
local session/streaming bridge is instrumented separately: unless image-token
activity shows that follow-up vision tokens were actually recomputed, the paper
describes that family as Q0 admission plus K-cache reuse, not as active
follow-up pruning. The completed long-bucket continuations measured that
boundary in the current prompt-cache path: all tested follow-up image tokens
were cache-served. That choice is deliberate.

\begin{sectiontodo}{Add the overview figure and final algorithm box}
The prose now matches the paper's current scope, but the final manuscript still
needs a compact visual that makes three distinctions obvious: first-pass
pruning, after-ingest prompt reuse, and Qwen routing as mechanism validation
rather than measured sparse execution.

\textcolor{todoBorder}{Source pointers: \path{src/codec_through/temporal.py},
\path{src/codec_through/novelty_pruning.py},
\path{src/codec_through/pruned_vision_tower.py},
\path{scripts/run_kv_cache_session.py},
\path{scripts/run_kv_selective_reprefill_v2.py},
\path{scripts/run_phase1_29_planner_accuracy_probe.py},
\path{paper/claim-matrix.md}.}
\end{sectiontodo}
