\section{Experimental Setup}

\subsection{Benchmarks and Workloads}

The paper uses three workload families, because the contribution is not a
single benchmark trick and the protocols are not interchangeable.

The routing mechanism is evaluated on sparse semantic-substitution holdouts:
TOMATO \cite{tomato} and a frozen motion-heavy MVBench slice \cite{mvbench}.
These are the cleanest settings for testing whether training-free temporal
reuse preserves answers at lower effective fresh-frame budgets under a fixed
dense backend.

The first-pass speedup story uses the MLX-community
\texttt{gemma-4-e4b-4bit} conversion of Google Gemma 4-E4B on Video-MME
\cite{gemma4e4b,gemma4e4bmlx,videomme}, MVBench, and TOMATO at 8-frame
settings, plus dev-expansion cells and deeper frame-count probes. The
after-ingest persistent-KV story uses repeated follow-up questions on Video-MME
sessions across short, medium, long, and deeper 32-frame slices, where the same
video is queried multiple times and prompt reuse is therefore meaningful.

The scale-out streaming and UI studies are kept separate from those benchmark
claims. They are native-rate deployment evidence, not replacements for the main
evaluation, and they become first-class scale-out tests only when the same
artifact standards and matched baselines are available.
By design, sparse routing uses pixel-diff on sampled decoded frames, while the
separate streaming lane uses H.264 metadata at native frame rate, including
FFmpeg motion-vector side data exported with \texttt{-flags2 +export\_mvs}
or current-build CLI \texttt{-export\_side\_data +mvs} / libavcodec
\texttt{export\_side\_data=mvs}, plus \texttt{codecview=mv=pf+bf+bb}
inspection paths \cite{ffmpegcodecs,ffmpegfilters}. The signals are protocol-specific, not
interchangeable.

\subsection{Models, Hardware, and Preprocessing}

The Qwen routing and persistent-KV experiments use Qwen2.5-VL-7B-Instruct-4bit
\cite{qwen25vl}, a frozen open-weight video VLM, through MLX-VLM
\cite{mlxvlm} on Apple Silicon. The dense wall-clock baseline and the
persistent-KV scaling curve use the same local stack on an M3 Air with
16\,GB unified memory. The first-pass vision-pruning results use the
MLX-community 4-bit conversion of Gemma 4-E4B \cite{gemma4e4b,gemma4e4bmlx},
a separate open VLM family, on the same general MLX environment. The scale-out
streaming evaluation uses a separate RTSP and screen-recording pipeline with a
Gemma 4 26B/A4B-family stack.

For benchmark comparability, the main-path runs use uniform global sampling at
8 frames and square-pad plus resize to 560\,$\times$\,560. The routing planner
operates on decoded RGB frames. Padding-aware reuse accounting is reported
separately from raw padded reuse in the artifact summaries; paper-facing
effective-budget numbers use active-region reuse rather than trivially static
padded borders.

\begin{table}[H]
\centering
\caption{Main evaluation lanes. The rows are protocol identifiers, not a
claim that all results share one denominator.}
\label{tab:setup-lanes}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabularx}{\linewidth}{@{}p{0.20\linewidth} p{0.23\linewidth} X p{0.20\linewidth}@{}}
\toprule
Lane & Model/runtime & Primary protocol & Main reported metric \\
\midrule
Routing & Qwen2.5-VL-7B-Instruct-4bit, MLX-VLM & TOMATO and MVBench
semantic-substitution holdouts & Accuracy/agreement at effective fresh-frame
budget \\
First-pass pruning & mlx-community/gemma-4-e4b-4bit and matched Qwen probes, MLX & Fresh-video
first query at 8f plus selected frame-count probes & First-query E2E, \(V_{\mathrm{share}}\),
\(V_{\mathrm{red}}\), accuracy delta \\
After-ingest reuse & Qwen2.5-VL-7B-Instruct-4bit, MLX-VLM & VideoMME sessions
with one cold query and two follow-ups & Paired drift, follow-up latency,
repair speedup \\
Scale-out streaming & Separate Gemma 4 26B/A4B-family RTSP / screen-recording stack &
Separate native-rate scale-out protocol & ViT-call reduction, throughput, diagnostics,
artifact-harmonization status \\
\bottomrule
\end{tabularx}
\end{table}

For local timing claims, the harness uses one wall-clock source per experiment,
forces the backend to finish work before stopping the timer, and reports the
denominator for every speedup. Follow-up speedups are median cold-follow-up
latency divided by median session-follow-up latency unless explicitly labeled
otherwise; first-pass rows are first-query end-to-end ratios. Paired
experiments keep clip order and compared conditions aligned, log raw per-query
records, and treat fanless-laptop thermal caveats as evidence labels rather
than as post-hoc excuses. The practical pairing rule is simple: compared arms
use the same manifest, frame count, scorer, and local wall-clock harness, and
the thermal label is determined from the logged non-target-stage timing deltas
rather than from whether the result is convenient. When a run is missing the
instrumentation needed for a mechanism claim, the manuscript says so or keeps
the result advisory.

\subsection{Metrics and Reporting Discipline}

We report different metrics for different regimes because the paper would be
misleading otherwise.

For Qwen routing, the paper reports accuracy, dense-versus-cached agreement,
parse failures, and effective fresh frames. For Gemma first-pass pruning, it
reports end-to-end speedup, vision-time reduction, accuracy delta, and the
share$\times$reduction prediction. For persistent-KV, it reports follow-up
latency, cold-versus-session speedup, prefix coverage, paired choice and
correctness drift, and accuracy delta between baseline and session modes. These
paired-drift metrics are stricter than aggregate accuracy: they ask whether the
same item gets the same parsed answer under reuse, not merely whether the total
score is unchanged.

All automated main-text assets are generated from checked-in artifact summaries.
If a result is clean, advisory, artifact-pending, or supplementary, the
manuscript says so explicitly instead of letting the build silently promote it.

For the adaptive C-PERSIST breadth result, the denominator is both query- and
session-visible. The combined envelope is 31 sessions \(\times\) three queries
per session \(=93\) paired queries, with 62 repaired follow-ups. The paper
reports the query-level no-observed-drift bound because the paired answer is
logged per query, and also reports the more conservative 0/31 session-level
view where any drift in a session would count against the session.
