\section{Native-Rate Streaming as a Deployment Target}

Streaming state reuse is the natural scale-out target for anti-recomputation:
the model revisits nearly the same visual state while deciding when to keep,
shift, rebuild, or invalidate cached state. We do not claim a standardized
C-STREAM result yet; here we report boundary evidence from a checked 26B-class
scale-out bundle: cache-correctness failures, positive small-\(N\)
prefix-snapshot rows, strong
low-FPS / screenshot / recency baselines, denominator-safe exactness exports,
and source manifests. The result is mixed in the scientifically useful way. It
shows which mechanisms are plausible, which simple baselines are serious, and
which cache paths are unsafe.

Unlike sparse-sampled benchmark runs, the streaming lane tests cache lifetime:
when to keep state, shift it, rebuild it, or declare it stale. The tested
scale-out stack exercises motion-vector and residual side-channel staleness
signals, sectional cache shifts, and event/inflection triggers. Those
mechanisms are why the lane is not merely an application demo. Its claims stay
separately labeled because native streams add evaluation problems that
VideoMME, MVBench, and TOMATO under-test: query cadence, scroll/pan, live-world
updates, stale-cache failure, fixed-vision-budget perception rate, and cache
topology under mixed sliding-window/full-attention attention.

The local Qwen session/streaming bridge explains why this gate matters. The
dense-first-query reference recovers aggregate first-query correctness and
reaches 2.79$\times$ paired speedup, missing the preregistered 3.0$\times$
rescue floor. The later instrumented cache-reuse rerun preserves the same
aggregate boundary and reaches 3.02$\times$, but still misses the follow-up
fidelity target. Instrumentation also shows that follow-up vision pruning is
inactive in that family: follow-up image tokens are cache-served rather than
actively pruned. The right interpretation is dense-first-query admission plus
cache-state reuse, not a validated native-rate sparse-vision backend.

The 26B rows explain why cache-correctness is a gate rather than bureaucracy.
The default cross-turn cache path over mixed sliding-window and full-attention
layers fails the cache-correctness check: it can move fast while producing
divergent text and answer choices. A runner-side correctness guard that fully
refills rotating-cache layers passes, and the patched library now passes the
full cache-correctness regression as well: 42/42 text-identical rows, zero choice or
correctness diffs, and four matched parse failures. That closes this
cache-correctness regression; it is not C-STREAM speedup. The patched path
refuses unsafe cross-turn trim and runs at roughly cold-dense wall-clock. A
topology-aware prefix snapshot is
the current positive scale-out follow-up row, but its denominator is narrow: the
reported 9.11$\times$ at 8f and
18.71$\times$ at 32f are per-follow-up medians after the prefix snapshot is
warm, not setup-inclusive session speedups. The 8f row has seven
multiple-choice prompts; five are parse-clean with 0/5 choice/correctness
diffs, and two have matched parse failures. The other 14 rows are open-ended
text-comparison rows, and 6/21 rows have text diffs. The expanded 32f row has seven
multiple-choice prompts with 0/7 choice/correctness diffs, plus 14 open-ended
text-comparison rows, 7/21 text diffs, and no parse failures. These are small-\(N\),
wrapper-specific rows, not proof that ordinary PromptCacheState is safe.

The same rows also answer a throughput question that streaming readers
naturally ask: on the warm follow-up wall-clock denominator, how many prompt
frames are effectively processed per second? The 8f prefix snapshot yields
27.02\,fps at the median, with 8/21 paired rows above 30\,fps. The expanded 32f
snapshot yields 54.68\,fps at the median, with 19/21 rows above 30\,fps and a
23.85--134.43\,fps range. Cold dense sits near 2--3\,fps on the same rows.
This is not a new correctness claim, not setup-inclusive speed, and not
C-STREAM closure: it is the same after-warm prefix-snapshot evidence expressed
in the fps denominator that native-stream work ultimately needs. The first query
still pays full dense visual processing, the snapshot wrapper is required for
the safe path, and continuous capture, stale-cache invalidation, and
desktop-agent scroll/pan traces remain future gates.

The streaming baselines cut in the other direction. On 22 screen/UI events,
low-FPS dense uses four uniformly spaced frames and matches the fresh oracle on
17/22 events, beating screenshot polling with one query-time frame (13/22),
recency last-\(K\) with four recent frames (12/22), and the tested
event-window proxy with four event-window frames (13/22). That does not kill
C-STREAM; it clarifies the denominator. Fixed-evidence quality is not where the
tested proxy wins. The fps view above shows why the native-rate denominator is
still worth measuring, but the evaluated bundle has not yet earned the stronger
streaming claim. Advisory predecessor sectional-scroll instrumentation, not
part of the checked bundle table, points in the same direction qualitatively:
over the same recording duration, event-driven state reuse can perceive at
decode cadence with far fewer vision fires than polling. Because those raw rows
are not part of the evaluated bundle, we do not use their exact multiplier as
C-STREAM evidence. That axis still needs checked native mechanism-quality
validation before it becomes a headline.

The recovery path is therefore specific, not rhetorical. C-STREAM needs a
policy that wins on the axis native streams actually own: higher
perception-rate at the same vision budget while preserving event-window
answers. The tested proxy failed because its event windows were not enough to
beat a simple four-frame dense baseline; the default cache path failed because
mixed sliding-window/full-attention cache topology made cross-turn state
semantically unsafe; and post-vision-tower pruning failed as systems evidence
because it skipped work after the expensive stage had already run. A positive
C-STREAM result should combine topology-safe state reuse, an event/staleness
gate that beats low-FPS dense under matched event windows, and a stale-cache
failure case that shows when the runtime deliberately buys fresh evidence.

\input{generated/tables/scaleout_bundle_status.tex}

The scale-out bundle also adds two useful boundary checks. First, the large
feature-reuse export is now denominator-safe: zero correctness delta is logged
on 1,937 sparse-sampled rows, while byte-identical raw-paired text is verified
on 513 rows. Those are separate claims. Second, post-vision-tower hard pruning
on the 26B stack is a negative systems result: because the full vision tower has
already run, policy overhead can dominate, so the row is not evidence for real
sparse-ViT speedup. It is a reminder that the paper's C-CEILING arithmetic
assumes the accelerated stage is actually skipped and the policy overhead is
small.
