\section{Limitations and Reproducibility}

The paper makes three kinds of claim, and each one breaks differently. That is
the main limitation to manage.

For first-pass Gemma pruning, the evidence is now good enough for a main
results section, but not every cell is equally clean. VideoMME is clean.
MVBench and TOMATO are advisory because the measured gains survive, but the
thermal caveats are still visible and should remain visible in the text.
Architecture breadth is still asymmetric, but no longer Gemma-only. The
first-pass measured headline cells are still Gemma-first today, while a
matched Qwen cross-architecture probe now shows the same ceiling binding at a
smaller absolute lift. The n=60 stacked-regime composition audit also closes one
tempting overclaim: composition does not outrun the ceiling. The local stacked
cell is ceiling-matched, which is useful evidence for the arithmetic and a
null on super-ceiling composition.

The measured sparse-execution story is now more concrete but still bounded.
Gemma supplies the cleanest current operating point: 32f short skips timed
vision-tower work at 1.316$\times$ first-query speedup with no paired drift and
no parse failures on 20 items. The full Gemma 8/16/32f sweep has zero paired
answer drift, but dense and sparse arms share parse failures in some cells and
the 8f row misses the ceiling tolerance. Qwen supplies the complementary
boundary: aggressive 16f pruning collapses fidelity and format, while
\(kr=0.85\) restores fidelity, format, and ceiling agreement at only
1.032$\times$ end-to-end speedup and 13.6\% vision-time reduction. The paper
therefore claims a measured sparse-vision envelope, not a broad
fidelity-preserving sparse backend.

For persistent-KV, the numbers are much larger, but the regime is narrower.
These are \emph{after-ingest} claims: the first query on the video still pays
full freight, and the gain only appears when subsequent questions concern that
same video. The tested envelope is also finite. Through 16 frames the local
curve stays inside the current 7B tested envelope, with a clean 16f point and an
8f point that remains within the preregistered accuracy criterion despite
\(\Delta\)acc \(=-0.048\). Beyond that, unrepaired fidelity degrades
quickly. The 3B story is wider but weaker: it holds a tolerated $-0.19$
pre-basin plateau through 36f / 14.5k prefill tokens rather than preserving the
clean 7B envelope, and the current mechanism story is threshold onset plus
basin geometry rather than an architecture-specific saturation ceiling.

Selective re-prefill narrows that limitation but does not erase it. Fixed
\(K=1\) is now a real local repair envelope, with no observed paired drift on
93 paired queries across short, medium, long, and 32-frame short slices and no
observed pathological outputs across 62 repaired follow-ups. The rule-of-three
upper bound on an unseen query-level paired-drift rate is still about 3.2\%;
the more conservative session-level view is 0/31 sessions with any drift, or
about 9.7\%. The claim remains ``no observed paired drift,'' not
population-level exactness. The
long-bucket cell also preserves a weak 7/21 cold baseline; that is fidelity
evidence under a hard regime, not evidence that the model itself understands
long VideoMME well. The adaptive repaired-cache inheritance result is now
the stronger breadth result rather than a short-only curiosity: it covers the
same 93 paired queries with no observed paired drift and 14.90--35.92$\times$
same-class follow-up speedup; the cold-all-query versus repaired-follow-up
ratio is 15.28--35.97$\times$. Its remaining caveats are different. The long and
32f cells passed the science gates but exceeded preregistered RSS gates that
were too tight relative to later observed memory; the paper should report the
observed memory envelope rather than retroactively calling those runs failures.
The original breadth result is finite-horizon because those sessions contain
two follow-up questions. The separate many-turn stress closes the easiest
version of that attack: adaptive repaired-cache inheritance and scheduled refresh have no
observed drift through a 50-turn repeated-question cycle on seven short videos.
That is still not a natural-dialogue stability proof; it is a controlled
cache-horizon stress with deterministic dense replicas for turn-matched
pairing.

\IfFileExists{generated/tables/memory_characterization.tex}{
\input{generated/tables/memory_characterization.tex}
}{
\draftnote{Run \texttt{make paper-sync} to generate the memory characterization table.}
}

The related-work bar for this lane is also higher than ``we reused a KV
cache.'' Prefix caching, RadixAttention, CacheBlend-style repair, SparseVILA,
and HERMES all make parts of that sentence prior art. The manuscript's current
claim is narrower: video-specific visual-tail repair, paired-drift accounting,
the cache-basin failure mode, and the repaired-cache inheritance rule on this
local stack. A submission version should still add at least one matched
head-to-head against the closest persistent-video or visual-token sparsity
baselines.

For Qwen routing, the opposite caveat applies. The holdout evidence is clean
and useful, but it is still a quality--compute frontier result under a fixed
dense backend. It should not be inflated into a measured sparse-execution
speedup claim until the backend actually skips timed work. The same caution now
applies to the Qwen VideoMME frame-count story: the dev-split 16f long-bucket
regression does not replicate on disjoint holdout, so the manuscript treats it
as a dev-only shape rather than a universal scaling law. The 1.57 feature-drift
geometry itself now reproduces on holdout at 8f and 16f; what failed to
transfer was the downstream long-bucket accuracy shape, not the drift signal.

The streaming/deployment lane remains the least harmonized evidence class in
the paper, even though it is the clearest candidate for a future C-STREAM claim.
It is there because it names the practical regime where redundancy can become
large, not because it already closes the full systems-reviewer checklist. The
checked scale-out bundle is now real and useful, but mixed: default 26B
cross-turn cache reuse is unsafe, a topology-aware prefix snapshot is positive
only at small \(N\), fixed-evidence stream baselines favor low-FPS dense over
the current event-window proxy, and post-vision-tower hard pruning shows that policy
overhead can erase any expected win if vision work was not actually skipped.
The Qwen composition bridge now exists and is useful precisely because it is
diagnosed rather than promoted:
the original stack reproduced speedup but lost accuracy,
dense-first-query admission restores Q0 aggregate correctness but misses the
3-query rescue gate, and the offline admission frontier contains an oracle
rescue point but no deployable format-clean policy in the current endpoint
family. The long-bucket admission sweep then
falsifies every tested Q0 keep rate from 0.67 to 0.90 and empirically confirms
that follow-up vision pruning is inactive under prompt-cache reuse in that arm.
At high keep rates, aggregate Q0 accuracy recovers while follow-up accuracy
still drops, so the failure is downstream of first-query aggregate correctness
and tied to the follow-up state. The completed cache-invalidated follow-up test
sharpens the boundary: forcing follow-up V-pruning to be active collapses the
speedup to 1.06$\times$ and still lands on the same net aggregate loss as
cache reuse, while any-paired-drift sets differ. That is informative even
before the tensor-level mechanism is isolated: it falsifies a single-row-set
explanation and localizes the boundary to follow-up state quality rather than
first-query aggregate correctness alone. The current post-hoc attribution
passes its preregistered gates, but it is not a causal tensor probe. Dense
logit-margin and richer-feature scouts add a useful negative: answer-letter
margin has signal (held-out AUC about 0.71), but margin alone gives too little
coverage for a high-precision guard, and adding entropy, turn index, duration,
prompt length, and policy source still fails the preregistered deployable-guard
bar. The nominal label-free feature in that artifact is empirically
answer-aware, so the result should not be sold as a runtime guard. The next
proof step is direct cache-state instrumentation plus genuinely independent
state features. A related
local codec-native bridge remains scientifically interesting, and the latest
1.29 results now provide semantic
planner-substitution evidence: MAX-over-span sparse sampling is hard-falsified,
but the continuous-score redesign matches dense choices on VideoMME dev
all-duration \(n=30\) and later calibration-mode/source ablations are neutral
on the local slices we ran. This remains a semantic planner result, not a
latency win; the offline extraction path took 7290 s and the deployment path
still needs streaming decoder integration.

The current benchmark mix also under-samples scroll and pan regimes. We audited
this directly on a 60-item VideoMME stratification across 8f/16f/32f and found
0/60 items above a relaxed \texttt{shifted\_fraction} \(\geq 0.30\) gate, with
max shifted fraction 0.125. That does not certify C-VISION on sustained
egomotion or scrolling content; it shows VideoMME is the wrong corpus for that
question. A scroll/pan characterization now requires EgoSchema, EPIC-Kitchens,
Ego4D, or a labeled synthetic set.

A dynamic-compute runtime also creates a robustness surface we have not yet
measured. Inputs can amplify apparent novelty and force the system to spend
more compute seeing: flicker, rolling-shutter bands, blinking UI, repetitive
local motion, scene-cut bursts, camera shake, and sensor desynchronization are
all future stressors. The right metrics are novelty amplification, latency
amplification, deadline miss rate, and fallback behavior. Until that suite
exists, the speedups in this paper are workload-regime results, not worst-case
latency guarantees.
The dual failure also matters: an input can hide a task-critical change below
the refresh trigger and cause stale reuse rather than excessive recompute. A
real robustness suite needs both denial-of-savings and denial-of-freshness
cases.

Simple dense baselines are also not strawmen. A 4f cold-dense baseline over the
same 57-session / 171-query VideoMME union is only 1.21$\times$ faster than 8f
and has ambiguous overall accuracy delta, but it is a real competitor in some
duration buckets and a hard short-bucket failure. That is why future C-STREAM
and C-VISION claims need matched low-FPS dense controls rather than only
same-method ablations.

Finally, equal aggregate accuracy is not the same as identical behavior. The
Gemma routing split makes this visible: TOMATO passes the agreement gate, while
MVBench preserves aggregate accuracy but changes 8/30 choices across four
motion subgroups. The composition and selective-reprefill drift audits show the same pattern in
different forms. Reviewers should read the paired-drift columns as part of the
claim, not as decorative diagnostics.

The persistent-cache failures should also be read as attention-context or
cache-state failures, not as positional-encoding drift claims. The recurring
failure mode is not just stale pixels; it is incoherent internal state. Fresh
and cached mixtures must preserve cache topology, positions, and layer
semantics, or they can move fast while answering the wrong question. The current
experiments identify when reused state changes later answers; they do not yet
isolate a unique internal mechanism without direct cache-state instrumentation.

Architecture exposure is another limitation and a design lesson. Qwen is the
high-stability local family for routing and persistent-cache follow-up reuse.
Gemma is the primary first-pass vision-pruning family and exposes a useful
vision-tower sparse path, but Gemma adaptive persistent-cache reuse remains
blocked by sliding-window / rotating-cache semantics in the current MLX stack.
Future VLM runtimes should expose stable cache semantics, cache invalidation
controls, vision-tower keep masks, per-stage timing, token geometry, and
cache-state diagnostics as first-class interfaces. Those hooks are not just
engineering convenience; they decide which anti-recomputation claims can be
tested without risking silent cache corruption.

\begin{table}[H]
\centering
\caption{Architecture lessons from the current evidence. This is not a model
leaderboard; it is a runtime-interface lesson about which reuse claims can be
tested cleanly.}
\label{tab:architecture-lessons}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabularx}{\linewidth}{@{}p{0.18\linewidth} X X@{}}
\toprule
Family & What it currently supports & Design lesson \\
\midrule
Qwen2.5-VL-7B & Stable routing and persistent follow-up reuse; strong
selective re-prefill evidence; measured sparse-vision configuration boundary &
Expose stable cache semantics, cache diagnostics, and frame-tail repair hooks. \\
Gemma 4-E4B & First-pass vision-pruning measurements; clean measured
sparse-vision 32f-short operating point plus broader zero-drift sweep with
format caveats & Expose keep masks and per-stage timing, but make
rotating/sliding cache behavior explicit. \\
Candidate C-STREAM & Native-rate streaming state reuse under a separate
protocol; checked bundle with cache-correctness, prefix snapshot, fixed-evidence
baselines, and exactness export & Promote only after the native streaming
policy beats low-FPS/screenshot/recency baselines under the same quality
envelope and cache topology. \\
\bottomrule
\end{tabularx}
\end{table}

The paper is nevertheless being built to be reproducible. Automated main-text
figures and tables are generated from checked-in artifact summaries or from
checked-in paper figures, the appendix records the repo commits used for the
sync, and advisory or artifact-pending evidence is labeled as such instead of being
silently promoted into the headline figures. The paper builds locally with the
checked-in \texttt{make paper-*} targets plus `tectonic` or a fuller TeX
stack.

\begin{sectiontodo}{Freeze the public artifact and release language}
Before submission, this section still needs the final public-release sentence,
artifact-bundle wording, and one last pass on which advisory results stay in
main text versus move to the appendix.

\textcolor{todoBorder}{Source pointers: \path{paper/priority.md},
\path{paper/claim-matrix.md},
\path{docs/reproduction-status.md},
\path{docs/methodology/performance.md},
\path{docs/clip-policy.md},
\path{research/experiments/2026/2026-04-23-phase-1_60-corpus-limitation-findings.md},
\path{research/experiments/2026/2026-04-23-phase-1_29B-codec-native-replication-prereg.md},
\path{research/experiments/2026/2026-04-24-phase-1_30W-q0-dense-followup-pruned-full-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_30Z-long-q0-kr067-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_30AB-long-q0-sweep-findings.md},
\path{research/experiments/2026/2026-04-24-phase-1_55D-selective-reprefill-v2-k1-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_55G-k1-medium-replication-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_55F-q3-post-q2-state-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_55I-k1-long-replication-findings.md},
\path{research/experiments/2026/2026-04-25-phase-1_55H-k1-32f-short-probe-findings.md},
\path{research/experiments/2026/artifacts/phase1_55K_adaptive_temperature_sweep/},
\path{research/experiments/2026/artifacts/phase1_63G_gemma_track_b/},
\path{research/experiments/2026/artifacts/phase1_63H_16f_kr_sweep/},
\path{research/experiments/2026/artifacts/phase1_65_logit_margin_failure_predictor/},
\path{research/experiments/2026/artifacts/phase1_66_memory_characterization/}.}
\end{sectiontodo}
