\section{Conclusion}

The paper began with a small absurdity: much of the video did not change, and
the model paid anyway. The measured answer is not one single multiplier. Fresh
videos admit modest but real first-pass gains, and those gains obey a
share-limited ceiling that explains the regime and binds cleanly on the core
ceiling checks, including the matched Qwen cross-architecture probe and the
new measured sparse-vision envelope. Gemma now supplies the cleanest timed-skip
cell at 32f short: 1.316$\times$ first-query speedup with no paired drift and
no parse failures on 20 items. Qwen supplies the cautionary half of the same
story: aggressive pruning fails, while a conservative keep rate restores
fidelity at low gain.
Same-video
follow-up queries admit much larger multipliers: raw persistent-KV reuse
reaches sub-second latency inside the \(\leq 16\)f tested envelope, while
selective re-prefill repairs the deeper cache-reuse basin at higher latency.
Adaptive repair now gives no observed paired drift across 93 paired queries
at 3.20--6.51\,s repaired follow-up median and 14.90--35.92$\times$
same-class follow-up speedup; the cold-all-query versus repaired-follow-up
ratio is 15.28--35.97$\times$. Fixed \(K=1\) remains the no-coordination
baseline at 9.48--20.37$\times$ same-class follow-up speedup on the same
breadth. The many-turn stress adds the missing horizon check: adaptive and
scheduled-refresh reuse stay drift-free through a 50-turn repeated-question
cycle, while fixed \(K=1\) shows nonzero repeated-question drift but no cliff.
Candidate
C-STREAM remains the right scale-out target: perception-rate streaming state
reuse under a native-rate protocol. The checked 26B-class scale-out bundle is now mixed
evidence rather than pending evidence: default cache reuse is unsafe,
prefix-snapshot follow-up rows are positive but small-\(N\), fixed-evidence
baselines favor low-FPS dense over the current event-window proxy, and
exactness claims must keep the 1,937 zero-accuracy-delta and 513 byte-identical
denominators separate.

The scientific value is in the boundaries as much as in the wins.
Local diagnostics suggest fresh-compute placement over time is not captured by
novelty magnitude alone,
aggregate accuracy can hide answer-identity drift, and semantic substitution
must not be confused with measured sparse execution.

What remains is a broader fidelity-preserving sparse-backend curve, natural
multi-turn dialogue stress, cleaner native-streaming systems baselines, and
causal guard features beyond the current cache-distance probe. The n=60
composition audit, the long-bucket admission sweep, the cache-invalidated
follow-up test, and the direct K/V distance audit already closed the
multiply-the-headlines temptation: the gains do not stack naively. The useful question now is
where each ceiling moves in the architectures and deployment protocols people
actually care about.

It also leaves a larger media agenda. The current paper is not an AI-native
codec and does not claim one. It shows why that direction is worth studying:
VLMs should not have to reverse-engineer every repeated frame back into state.
Future media streams for machines could expose change, motion, uncertainty,
objects, text, sensor time, and active tiles directly. Anti-recomputation is
one empirical step from video-as-frames toward video-as-world-state updates.
The strongest future version is not a better pixel threshold; it is a
model-facing media interface where change, motion, object state, sensor time,
and uncertainty arrive as first-class evidence.

\begin{sectiontodo}{Shorten this once the venue template and abstract freeze}
The conclusion now carries both the measured paper and the larger
VLM-native-media agenda. The final pass should make it tighter, not louder, and
must keep the future-codec language clearly separated from current evidence.

\textcolor{todoBorder}{Source pointers: \path{paper/priority.md},
\path{paper/claim-matrix.md},
\path{paper/publishability-status.md}.}
\end{sectiontodo}
