\begin{thebibliography}{99}

\bibitem{codecsight}
Yulin Zou, Yan Chen, Wenyan Chen, JooYoung Park, Shivaraman Nitin, Luo Tao,
Francisco Romero, and Dmitrii Ustiugov.
\emph{CodecSight: Leveraging Video Codec Signals for Efficient Streaming VLM
Inference}. arXiv:2604.06036, 2026.

\bibitem{copevideolm}
Sayan Deb Sarkar, R\'emi Pautrat, Ondrej Miksik, Marc Pollefeys, Iro Armeni,
Mahdi Rad, and Mihai Dusmanu.
\emph{CoPE-VideoLM: Leveraging Codec Primitives For Efficient Video Language
Modeling}. arXiv:2602.13191, 2026.

\bibitem{coviar}
Chao-Yuan Wu, Manzil Zaheer, Hexiang Hu, R. Manmatha, Alexander J. Smola, and
Philipp Kr\"ahenb\"uhl.
\emph{Compressed Video Action Recognition}. CVPR 2018; arXiv:1712.00636.
Pages 6026--6035. doi:10.1109/CVPR.2018.00631.

\bibitem{cacheblend}
Jiayi Yao, Hanchen Li, Yuhan Liu, Siddhant Ray, Yihua Cheng, Qizheng Zhang,
Kuntai Du, Shan Lu, and Junchen Jiang.
\emph{CacheBlend: Fast Large Language Model Serving for RAG with Cached
Knowledge Fusion}. EuroSys 2025; arXiv:2405.16444.

\bibitem{dejavu}
Jinwoo Hwang, Daeun Kim, Sangyeop Lee, Yoonsung Kim, Guseul Heo, Hojoon Kim,
Yunseok Jeong, Tadiwos Meaza, Eunhyeok Park, Jeongseob Ahn, and Jongse Park.
\emph{D\'ej\`a Vu: Efficient Video-Language Query Engine with Learning-based
Inter-Frame Computation Reuse}. PVLDB 18(10):3284--3298, 2025;
arXiv:2506.14107.

\bibitem{eventful}
Matthew Dutson, Yin Li, and Mohit Gupta.
\emph{Eventful Transformers: Leveraging Temporal Redundancy in Vision
Transformers}. ICCV 2023, pages 16911--16923; arXiv:2308.13494.

\bibitem{evoprune}
Yuhao Chen, Bin Shan, Xin Ye, and Cheng Chen.
\emph{EvoPrune: Early-Stage Visual Token Pruning for Efficient MLLMs}.
arXiv:2603.03681, 2026.

\bibitem{fastv}
Liang Chen, Haozhe Zhao, Tianyu Liu, Shuai Bai, Junyang Lin, Chang Zhou, and
Baobao Chang.
\emph{An Image is Worth 1/2 Tokens After Layer 2: Plug-and-Play Inference
Acceleration for Large Vision-Language Models}. ECCV 2024 Oral;
pages 19--35. doi:10.1007/978-3-031-73004-7\_2. arXiv:2403.06764.

\bibitem{fastvid}
Leqi Shen, Guoqiang Gong, Tao He, Yifeng Zhang, Pengzhang Liu, Sicheng Zhao,
and Guiguang Ding.
\emph{FastVID: Dynamic Density Pruning for Fast Video Large Language Models}.
NeurIPS 2025 poster; arXiv:2503.11187; OpenReview:
\url{https://openreview.net/forum?id=2xS4VtpApy}.

\bibitem{fastvlm}
Pavan Kumar Anasosalu Vasu, Fartash Faghri, Chun-Liang Li, Cem Koc, Nate
True, Albert Antony, Gokula Santhanam, James Gabriel, Peter Grasch, Oncel
Tuzel, and Hadi Pouransari.
\emph{FastVLM: Efficient Vision Encoding for Vision Language Models}. CVPR
2025, pages 19769--19780; arXiv:2412.13303.

\bibitem{flashvid}
Ziyang Fan, Keyu Chen, Ruilong Xing, Yulin Li, Li Jiang, and Zhuotao Tian.
\emph{FlashVID: Efficient Video Large Language Models via Training-free
Tree-based Spatiotemporal Token Merging}. ICLR 2026 Oral; arXiv:2602.08024;
OpenReview: \url{https://openreview.net/forum?id=H6rDX4w6Al}.

\bibitem{framefusion}
Tianyu Fu, Tengxuan Liu, Qinghao Han, Guohao Dai, Shengen Yan, Huazhong Yang,
Xuefei Ning, and Yu Wang.
\emph{FrameFusion: Combining Similarity and Importance for Video Token
Reduction on Large Vision Language Models}. In \emph{Proceedings of the
IEEE/CVF International Conference on Computer Vision (ICCV)}, pages
22654--22663, 2025; arXiv:2501.01986.

\bibitem{mvbench}
Kunchang Li, Yali Wang, Yinan He, Yizhuo Li, Yi Wang, Yi Liu, Zun Wang, Jilan
Xu, Guo Chen, Ping Luo, Limin Wang, and Yu Qiao.
\emph{MVBench: A Comprehensive Multi-modal Video Understanding Benchmark}.
CVPR 2024, pages 22195--22206; arXiv:2311.17005.

\bibitem{ffmpegcodecs}
FFmpeg. \emph{FFmpeg Codecs Documentation: \texttt{export\_mvs} and motion
vector side data}. \url{https://ffmpeg.org/ffmpeg-codecs.html}. Accessed
2026-04-29.

\bibitem{ffmpegfilters}
FFmpeg. \emph{FFmpeg Filters Documentation: \texttt{codecview}}.
\url{https://ffmpeg.org/ffmpeg-filters.html}. Accessed 2026-04-29.

\bibitem{mpegvcm}
MPEG. \emph{MPEG-AI, ISO/IEC 23888, Part 2: Video coding for machines}.
Status ongoing. \url{https://www.mpeg.org/standards/MPEG-AI/2/}. Accessed
2026-04-29.

\bibitem{jpegai}
JPEG. \emph{JPEG AI}. \url{https://jpeg.org/jpegai/}. Accessed 2026-04-29.

\bibitem{jpegxe}
JPEG. \emph{JPEG XE activity status}.
\url{https://jpeg.org/items/20241121_jpeg_xe_activity_status.html}. Accessed
2026-04-29.

\bibitem{hermes}
Haowei Zhang, Shudong Yang, Jinlan Fu, See-Kiong Ng, and Xipeng Qiu.
\emph{HERMES: KV Cache as Hierarchical Memory for Efficient Streaming Video
Understanding}. ACL 2026 Main; arXiv:2601.14724.

\bibitem{llavaprumerge}
Yuzhang Shang, Mu Cai, Bingxin Xu, Yong Jae Lee, and Yan Yan.
\emph{LLaVA-PruMerge: Adaptive Token Reduction for Efficient Large Multimodal
Models}. ICCV 2025, pages 22857--22867; arXiv:2403.15388.

\bibitem{dolbyatmos}
Library of Congress. \emph{Dolby Atmos Master File}.
\url{https://www.loc.gov/preservation/digital/formats/fdd/fdd000646.shtml}.
Accessed 2026-04-29.

\bibitem{mpeg4visual}
Library of Congress. \emph{MPEG-4, Visual Coding, Main Profile}.
\url{https://www.loc.gov/preservation/digital/formats/fdd/fdd000048.shtml}.
Accessed 2026-04-29.

\bibitem{quickvideo}
Benjamin Schneider, Dongfu Jiang, Chao Du, Tianyu Pang, and Wenhu Chen.
\emph{QuickVideo: Real-Time Long Video Understanding with System Algorithm
Co-Design}. Transactions on Machine Learning Research, 2026;
arXiv:2505.16175; OpenReview:
\url{https://openreview.net/forum?id=Rpcxgzcsuc}.

\bibitem{rekv}
Shangzhe Di, Zhelun Yu, Guanghao Zhang, Haoyuan Li, Tao Zhong, Hao Cheng,
Bolin Li, Wanggui He, Fangxun Shu, and Hao Jiang.
\emph{Streaming Video Question-Answering with In-context Video KV-Cache
Retrieval}. ICLR 2025; arXiv:2503.00540.

\bibitem{rinardapprox}
Martin C. Rinard. \emph{Approximate Computing}. CSAIL research overview.
\url{https://people.csail.mit.edu/rinard/research/ApproximateComputing/}.
Accessed 2026-04-29.

\bibitem{sglang}
Lianmin Zheng, Liangsheng Yin, Zhiqiang Xie, Chuyue Sun, Jeff Huang, Cody Hao
Yu, Shiyi Cao, Christos Kozyrakis, Ion Stoica, Joseph E. Gonzalez, Clark
Barrett, and Ying Sheng.
\emph{SGLang: Efficient Execution of Structured Language Model Programs}.
NeurIPS 2024; arXiv:2312.07104.

\bibitem{sparsevlm}
Yuan Zhang, Chun-Kai Fan, Junpeng Ma, Wenzhao Zheng, Tao Huang, Kuan Cheng,
Denis A. Gudovskiy, Tomoyuki Okuno, Yohei Nakata, Kurt Keutzer, and Shanghang
Zhang.
\emph{SparseVLM: Visual Token Sparsification for Efficient Vision-Language
Model Inference}. In \emph{Proceedings of the 42nd International Conference
on Machine Learning (ICML)}, PMLR 267:74840--74857, 2025;
arXiv:2410.04417.

\bibitem{sparsevila}
Samir Khaki, Junxian Guo, Jiaming Tang, Shang Yang, Yukang Chen, Konstantinos
N. Plataniotis, Yao Lu, Song Han, and Zhijian Liu.
\emph{SparseVILA: Decoupling Visual Sparsity for Efficient VLM Inference}.
ICCV 2025, pages 23784--23794; arXiv:2510.17777.

\bibitem{simplestream}
Yujiao Shen, Shulin Tian, Jingkang Yang, and Ziwei Liu.
\emph{A Simple Baseline for Streaming Video Understanding}. arXiv:2604.02317,
2026.

\bibitem{sttm}
Jeongseok Hyun, Sukjun Hwang, Su Ho Han, Taeoh Kim, Inwoong Lee, Dongyoon Wee,
Joon-Young Lee, Seon Joo Kim, and Minho Shim.
\emph{Multi-Granular Spatio-Temporal Token Merging for Training-Free
Acceleration of Video LLMs}. ICCV 2025, pages 23990--24000;
arXiv:2507.07990.

\bibitem{streamingllm}
Guangxuan Xiao, Yuandong Tian, Beidi Chen, Song Han, and Mike Lewis.
\emph{Efficient Streaming Language Models with Attention Sinks}. ICLR 2024;
arXiv:2309.17453.

\bibitem{streamingvlm}
Ruyi Xu, Guangxuan Xiao, Yukang Chen, Liuning He, Kelly Peng, Yao Lu, and Song
Han.
\emph{StreamingVLM: Real-Time Understanding for Infinite Video Streams}.
arXiv:2510.09608, 2025.

\bibitem{tomato}
Ziyao Shangguan, Chuhan Li, Yuxuan Ding, Yanan Zheng, Yilun Zhao, Tesca
Fitzgerald, and Arman Cohan.
\emph{TOMATO: Assessing Visual Temporal Reasoning Capabilities in Multimodal
Foundation Models}. arXiv:2410.23266, 2024.

\bibitem{tome}
Daniel Bolya, Cheng-Yang Fu, Xiaoliang Dai, Peizhao Zhang, Christoph
Feichtenhofer, and Judy Hoffman.
\emph{Token Merging: Your ViT But Faster}. ICLR 2023; arXiv:2210.09461.

\bibitem{videomme}
Chaoyou Fu, Yuhan Dai, Yongdong Luo, Lei Li, Shuhuai Ren, Renrui Zhang, Zihan
Wang, Chenyu Zhou, Yunhang Shen, Mengdan Zhang, Peixian Chen, Yanwei Li,
Shaohui Lin, Sirui Zhao, Ke Li, Tong Xu, Xiawu Zheng, Enhong Chen, Caifeng
Shan, Ran He, and Xing Sun.
\emph{Video-MME: The First-Ever Comprehensive Evaluation Benchmark of
Multi-modal LLMs in Video Analysis}. CVPR 2025, pages 24108--24118;
arXiv:2405.21075.

\bibitem{visionzip}
Senqiao Yang, Yukang Chen, Zhuotao Tian, Chengyao Wang, Jingyao Li, Bei Yu,
and Jiaya Jia.
\emph{VisionZip: Longer is Better but Not Necessary in Vision Language
Models}. arXiv:2412.04467, 2024.

\bibitem{vlcache}
Shengling Qin, Hao Yu, Chenxin Wu, Zheng Li, Yizhong Cao, Zhengyang Zhuge,
Yuxin Zhou, Wentao Yao, Yi Zhang, Zhengheng Wang, Shuai Bai, Jianwei Zhang,
and Junyang Lin.
\emph{VLCache: Computing 2\% Vision Tokens and Reusing 98\% for
Vision-Language Inference}. arXiv:2512.12977, 2025.

\bibitem{vllm}
Woosuk Kwon, Zhuohan Li, Siyuan Zhuang, Ying Sheng, Lianmin Zheng, Cody Hao
Yu, Joseph E. Gonzalez, Hao Zhang, and Ion Stoica.
\emph{Efficient Memory Management for Large Language Model Serving with
PagedAttention}. SOSP 2023; arXiv:2309.06180.

\bibitem{vscan}
Ce Zhang, Kaixin Ma, Tianqing Fang, Wenhao Yu, Hongming Zhang, Zhisong Zhang,
Haitao Mi, and Dong Yu.
\emph{VScan: Rethinking Visual Token Reduction for Efficient Large
Vision-Language Models}. Transactions on Machine Learning Research, 2026;
arXiv:2505.22654; OpenReview:
\url{https://openreview.net/forum?id=KZYhyilFnt}.

\end{thebibliography}
