\section{Source Traceability and Provenance}

The manuscript uses evidence classes and labels them differently in the text.
\emph{Reproduced-here evidence} comes from checked-in \texttt{codec-through}
artifacts and backs the automated headline assets, the persistent-KV curve, and
the Qwen routing section. \emph{Advisory evidence} is checked in but misses a
clean promotion gate such as thermal pairing or a strict quality band.
\emph{Pending C-STREAM evidence} is not automated until a validated local bundle
lands. \emph{Hypotheses or moving results} may be discussed for context, but
they are not allowed into the default automated manuscript snapshot.

This appendix is where that distinction becomes audit-friendly. The repo
provenance table below records the commit pins observed by the manuscript sync
step. Because this draft commits generated paper assets, the primary row can
point to the pre-commit working-tree snapshot that produced the PDF; a
\texttt{-dirty} suffix means the PDF is a working-tree draft, not a
submission-frozen artifact bundle. The final release should regenerate this
table from a clean tag. Within the main text, numbers are written so they can
be traced back to one phase note and one artifact family. When a result is
excluded or downgraded on provenance grounds, the paper says so explicitly. The
best current examples are the MVBench \texttt{sticky4} refinement, Gemma's
matched-parse-failure sparse-vision sweep, and Qwen's conservative low-gain
sparse-vision boundary: all are scientifically useful, but none should be
silently promoted beyond the finite evidence class it actually earned.

\begin{table}[H]
\centering
\caption{Claim/protocol/evidence manifest for the main quantitative assets.}
\label{tab:claim-protocol-manifest}
\tiny
\setlength{\tabcolsep}{1.5pt}
\renewcommand{\arraystretch}{1.06}
\begin{tabularx}{0.99\linewidth}{@{}
  >{\raggedright\arraybackslash}p{0.12\linewidth}
  >{\raggedright\arraybackslash}X
  >{\raggedright\arraybackslash}p{0.14\linewidth}
  >{\raggedright\arraybackslash}p{0.25\linewidth}
@{}}
\toprule
Asset & Claim / protocol & Evidence class & Source / hardware \\
\midrule
Headline table & regime headline cells; first-pass vision-pruning holdout, measured sparse-vision envelope, and after-ingest follow-up & local clean + local advisory & Phases 1.51V, 1.55A/D/E/F/G/H/I/K, 1.63E/G/H; adaptive mechanism and stage-timing artifacts; Gemma/Qwen local stacks, MLX / M3 Air 16 GB \\
C-CEILING figure & C-CEILING / C-VISION scatter-back validation; first-pass holdout, n=60 stacked-regime audit, matched cross-arch probe, and measured sparse-vision boundary & local clean + local advisory + local boundary & ceiling data JSON; local Gemma and Qwen stacks plus checked-in TOMATO session-5 artifacts; 1.63E/G/H raw artifacts checked in \\
Measured sparse-vision tables & real timed vision-tower work skipped under Gemma and Qwen & local bounded systems evidence & Phase 1.63G Gemma 8/16/32f scaling and Phase 1.63H Qwen 16f keep-rate sweep; Qwen 1.63E 8f boundary \\
C-PERSIST figure & C-PERSIST tested envelope; after-ingest same-video follow-up & local & Phase 1.55A artifacts; Qwen 7B/3B-4bit, MLX / M3 Air 16 GB \\
C-PERSIST repair & 20f/32f same-video selective re-prefill & local bounded recovery & Phases 1.55D/E/F/G/H/I plus adaptive mechanism and stage-timing artifacts; Qwen 7B-4bit, VideoMME short/medium/long + 32f short \\
C-PERSIST sampler sweep & adaptive short-cell practical temperature robustness & local reviewer-defense evidence & Phase 1.55K artifacts; Qwen 7B-4bit, VideoMME short slice, \(T\in\{0.0,0.5,0.7,1.0,1.5\}\) \\
Routing frontier & sparse routing under dense backend & local & Phase 1.20/21/34/36 notes; Qwen 7B-4bit, MLX \\
Gemma routing boundary & second-architecture semantic substitution & local boundary & Phase 1.42 artifacts; Gemma 4-E4B-4bit, TOMATO/MVBench motion holdouts \\
Qwen stacked boundary & session/streaming composition plus cache-boundary attribution & local negative / boundary & Phase 1.30 root-cause + W/X/Y/Z/AB/AC/AD/AF artifacts; Qwen 7B-4bit, VideoMME dev+holdout \\
Paired drift table & paired choice/correctness drift summary & local analysis & Phase 1.61 drift summary built from landed 1.30, 1.42, and 1.55A artifacts \\
Logit-margin scout & dense answer-margin signal is insufficient as a high-precision drift guard & local negative / future guard feature & Phase 1.65 artifacts; 228 scored Qwen paired rows \\
Memory envelope & process working-set characterization across landed families & local reproducibility evidence & Phase 1.66 memory characterization; 78 cells across follow-up reuse, admission/composition, and measured sparse vision \\
Method / limitations & codec-native planner bridge; semantic planner substitution & local semantic evidence & Phase 1.29B artifacts; Qwen 7B-4bit, VideoMME dev/short slices; offline extraction, not latency \\
Candidate C-STREAM & native-rate streaming, live camera, and deployment-style follow-up & pending validated artifact bundle & hold until checked local bundle provides raw paired outputs, cache-correctness smoke, matched baselines, and source-path manifest \\
\bottomrule
\end{tabularx}
\end{table}

\begin{sectiontodo}{Freeze this provisional manifest into a submission artifact map}
Before submission, this appendix should expand the provisional manifest above
into a frozen claim-to-artifact map for every table and figure in the paper,
including final hardware strings, exact artifact bundle paths, and any rows
that still move between main text and appendix.

\textcolor{todoBorder}{Source pointers: \path{paper/claim-matrix.md},
\path{docs/reproduction-status.md},
\path{paper/publishability-status.md}, and the locally generated
repo-provenance table produced by \texttt{make paper-sync}.}
\end{sectiontodo}

\IfFileExists{generated/tables/repo_provenance.tex}{
\input{generated/tables/repo_provenance.tex}
}{
\draftnote{Run \texttt{make paper-sync} to generate the repo provenance table.}
}
